%\specialhead{Acknowledgements}
%\section*{Acknowledgements}
%\addcontentsline{toc}{section}{Acknowledgments}

%checklist:
%\begin{itemize}
%\item MST: A Yamilov, 
I am in awe of the patience and skill of Dr. Alexey Yamilov, a brilliant researcher and motivated teacher. He exhibits the optimal balance of guidance and free reign. %Available all hours of the day, and cares deeply about my progress. 
Dr. Yamilov helped me learn how to think and how to express those thoughts.

Dr. Hui Cao, Dr. Paul Parris, Dr. Greg Story, and Dr. Thomas Vojta have been vital to my success at Missouri University of Science and Technology. 
At the University of Wisconsin-Madison 
Dr. Mark Eriksson, %<maeriksson@facstaff.wisc.edu>
Dr. Thad Walker, %<tgwalker@wisc.edu>
Dr. Cavendish McKay, %<cavendish.mckay@marietta.edu>
%http://www.marietta.edu/~phys/faculty.html
and 
Dr. Bob Wilson %<wilson@math.wisc.edu>
provided excellent instruction and guidance. 
Dr. Richard Brualdi, %<brualdi@math.wisc.edu>
Dr. Jay Martin, %<martin@engr.wisc.edu>
Dr. Paul Milewski, %<milewski@math.wisc.edu>
%, Michael Winokur %<mwinokur@wisc.edu>
%Bruce 'the Information' Broker %<bbroker@library.wisc.edu>
and 
Dr. Fabian Waleffe %<waleffe@math.wisc.edu>
greatly helped my progress as an undergraduate. 
At Madison East 
Dr. Scott Eckel, %<seckel@madison.k12.wi.us>
Beth Torrison, % <btorrison@gmail.com>
Richard Ihle, 
Tim Murphy, %<tmurphy18@wi.rr.com>
and 
Cynthia Chin %<cchin@madison.k12.wi.us>
%  \item Flatland
were outstanding teachers.

During graduate school Tom Magruder, %<tom.magruder@us.army.mil>, 
Uttam Chowdhury, and Amrita Roy Chowdhury have provided hours of happy conversation. Fond memories have been created with all the graduate students, faculty, and staff. Much of what I have accomplished is due in no small part to my parents, without whom none of this would have been possible. 

I would like to acknowledge funding from the National Science Foundation. Computational resources of the Extreme Science and Engineering Discovery Environment (XSEDE) and Teragrid made this research feasible. Participation in conferences and summer schools on high performance computing were sponsored by the NSF and XSEDE. 
%Thanks to the computers, without which none of the computations would have been feasible.
My education has also been funded by the United States Veterans Administration.
